Reading Notes

### 2020-08-11 2pd.tex
more comments from boss meeting

With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment. %EJ: True- but we gotta make people feel this.

@@

@@

<gain insight into the limits of coarse graining>
%EJ: Nice. Attempting to reorder based on heirarchy
<use that science to help solve energy crisis???????>
<create models for new opv compounds>
<gain insight into the limits of coarse graining>
<develop new tools that help humans do science>
<create a workflow that will make creating new models more accessible>
<I don't know where to put this but I want a section on best practices>
%EJ: Learning and incorporating best practices might actually be a new facet of your work. Like, we can point to the computational research papers that show how this wasn't done so much in the past, but it's happening better now, and we're going to lean into it- I think it fits.
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
live coding, interactive \cite{Wilson2016}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}

@@

\subsection*{Molecular Dynamics}
%EJ: Here or above: Why MD the right tool?
<I am borrowing heavily from Mike's MD section, so I need to come back through and rewrite this>
<md in general>
classical physics
interactions between particles
non bonded/bonded/angles/dihedrals
integrates Newton's equations of motion to update the particle positions.
iterated until thermodynamic equilibrium
sample a thermodynamic ensemble
First MD simulation \cite{Alder1957} system of 108 particles, 200 collisions in one hour on an IBM-704.
Now GPUs 100 millions times faster
<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
protein folding \cite{levitt75}, other biological processes, polymers \cite{Gartner2019a}

@@

<how do I relate this to what I want to do??>
- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
using these tools will help me to me a more efficient developer.
It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need further testing as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer.
This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
<atom typing is a pain and doing it manually is bad cite foyer paper>

@@

<what's going to be hard?> 
maybe SMARTS SMILES won't work without careful choice of beads. This is a little annoying but still preferrable I think because at least the reasons may be understandable (the order of the beads matters) or chemically sensible (one SMILES string may contain another -- just as one chemical moeity may be composed of more submoeities <this is a word?>)

>>>>

With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment. %EJ: True- but we gotta make people feel this. Numbers money, time, etc

@@

%% think mosdef -- scale of the problem
%% talk about best practices -- monolithic indecipherable code
%% general vs specific -- make the thing that works right now

@@

%EJ: Nice. Attempting to reorder based on heirarchy
<use that science to help solve energy crisis???????>
<create models for new opv compounds>
<gain insight into the limits of coarse graining>
<develop new tools that help humans do science>
<create a workflow that will make creating new models more accessible>
<I don't know where to put this but I want a section on best practices>
%EJ: Learning and incorporating best practices might actually be a new facet of your work. Like, we can point to the computational research papers that show how this wasn't done so much in the past, but it's happening better now, and we're going to lean into it- I think it fits.
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
live coding, interactive \cite{Wilson2016}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}

@@

\subsection*{Molecular Dynamics}
%EJ: Here or above: Why MD the right tool?
%% morphology matters - thermodynamics that govern self assembly
%% the kinetics that follow the processing
%% we can see the dynamics -- kinetic arresting, (if we want to probe the processing, need the dynamics)
%% monte carlo inefficient for polymers - cluster moves, not parallelizable 
<I am borrowing heavily from Mike's MD section, so I need to come back through and rewrite this>
<md in general>
classical physics
interactions between particles
non bonded/bonded/angles/dihedrals
integrates Newton's equations of motion to update the particle positions.
iterated until thermodynamic equilibrium
sample a thermodynamic ensemble
First MD simulation \cite{Alder1957} system of 108 particles, 200 collisions in one hour on an IBM-704.
Now GPUs 100 millions times faster
<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
protein folding \cite{levitt75}, other biological processes, polymers \cite{Gartner2019a}

@@

<how do I relate this to what I want to do??>
- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
using these tools will help me to me a more efficient developer.
It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need further testing as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 %% frame gixstapose as a tool for reproducible, approachable science
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer.
This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
<atom typing is a pain and doing it manually is bad cite foyer paper>

@@

<what's going to be hard?> 
maybe SMARTS SMILES won't work without careful choice of beads. This is a little annoying but still preferrable I think because at least the reasons may be understandable (the order of the beads matters) or chemically sensible (one SMILES string may contain another -- just as one chemical moeity may be composed of more submoeities <this is a word?>)
coarse-graining NFAs might be hard--planar backbones and floppy side chains
